---
title: "Lab#1"
author: "Ifeoma Okonye"
date: "2024-01-25"
output: html_document
---

# Introduction 

This Markdown file will give a step by step breakdown of how I completed the Lab 1 practical assignment.

Here, I will:
* Create Data Objects,
* Create Dataframes, and
* Check and Remove stored objects.

## Creating Data Objects.

I created a _named numerical variable_ and created a *vector of even numbers*. Then I reported the produced data objects and applied functions to each object in two different code chunks.

### Code Chunk 1: Creating Variables.

```{r}
# Creating a named numerical variable
Num <- -28.52
Num

# creating a new vector of numbers 
EvenNum <- c(2,12,10,8,16,4,28,14,18,26,6,22,20,24)
EvenNum

```


### Code Chunk 2: Applying Functions.

``` {r}
# Functions on named numerical variable
abs(Num)
round(Num)

# Functions on vector of numbers
median(EvenNum)
max(EvenNum)
sum(EvenNum)
sort(EvenNum)
SEN <- sort(EvenNum)
SEN
```


## Creating Dataframes.

In a chunk of code, I created a dataframe showing the count of car brands in a dealership ***(not real data)***.

### Code Chunk 3: Creating Dataframes.

```{r}
SN <- 1:10
cars <- c('Toyota', 'Chevrolets', 'Mazda', 'Mercedes-Benz', 'Hyundai', 'Lexus', 'Jeep', 'Kia', 'Dodge', 'Bentley')
count <- c(10, 5, 20, 7, 3, 15, 8, 6, 4, 1)
ds <- data.frame(SN, cars, count)
ds
head(ds, 3)
dim(ds)
```

Next, I loaded the airquality dataset from the list of freely provided datasets in R.The dataset shows the New York Air Quality Measurements.

### Code Chunk 4: Loading Datasets.

```{r}
data(airquality)
df <- airquality
df
head(df, 5)
nrow(df)
ncol(df)
dim(df)
summary(df)
```


## Checking and Removing stored objects.



### Code Chunk 5: Check where objects are stored.

```{r}
ls()
rm(list = ls())
ls()
```


